\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-03-07 paper/static/game_stage.tex
Re writing paper  (#7)
* fix maths for two opponents

* prep to run donation with two opponents

* run only for two opponents

* run further memory one experiments

* change in two opponents

* payoffs run for mem one

* stop showing probabilities

* finilise two opponents phi

* remove two rounds two opponents simulation from script

* move two opponents two rounds and fix phi

* prep to run script

* set beta for memory one experiment

* prep to re-run memory one

* clean notebooks

* python script for mutation experiment

* fermi fix

* run for 10 ** 7

* add matlab files for mutation

* wr

    % %%%%% game stage %%%%%
    \node at (0, .7) (turns) {turn};

    \pic[BurntOrange] at (0, 0) (myman) {man};
    \node at (0, -.6) {B};
    \pic[RoyalBlue] at (0, -2) (myman) {man};
    \node at (0, -2.6) {F};

@@

    \node at (1.5, .7) (turn1) {1};
    \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (1.5, 1.7) (exit) {};
    \node[circle, draw] (C) at (1.5, -.6)  {$C$};
    \node[circle, draw] (D) at (1.5, -2.6) {$D$};

@@

    \node at (3, .7) (turn2) {2};
    \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (3, 1.7) (exit2) {};
    \node[circle, draw] (C2)at (3, -.6)  {$C$};
    \node[circle, draw] (D2) at (3, -2.6) {$D$};

@@

    \draw (turn1) edge[out=15, in=165, ->, thick] node [above] {$\delta$} (turn2);
    \draw (turn1) edge[out=90, in=-90, ->, thick] node [above, rotate=90] {$1 - \delta$} (exit);
    \draw (turn2) edge[out=90, in=-90, ->, thick] node [above right] {$1 - \delta$} (exit2);

    \node[circle] at (4, -.6) {$\dots$};
    \node[circle] at (4, -2.6) {$\dots$};

>>>>

    % %%%%% game stage %%%%%
    \node at (0, .7) (turns) {turns};

    \pic[BurntOrange] at (0, 0) (myman) {man};
    \node at (0, -.6) {B};
    \pic[cyan] at (0, -2) (myman) {man};
    \node at (0, -2.6) {F};

@@

    \node at (1.5, .7) (turn1) {\textbf{1}};
    % \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (1.5, 1.7) (exit) {};
    \node[circle, draw] (C) at (1.5, -.6)  {$C$};
    \node[circle, draw] (D) at (1.5, -2.6) {$D$};

@@

    \node at (3, .7) (turn2) {\textbf{2}};
    \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (3, 1.7) (exit2) {};
    \node[circle, draw] (C2)at (3, -.6)  {$C$};
    \node[circle, draw] (D2) at (3, -2.6) {$D$};

@@

    \draw (turn1) edge[out=15, in=165, ->, thick] node [above] {\tiny{$\delta$}} (turn2);
    \draw (turn2) edge[out=90, in=-90, ->, thick] node [above right] {\tiny{$(1 - \delta)$}} (exit2);

    \node at (4, .7) (turn3) {$\dots$};
    \node[circle] at (4, -.6) {$\dots$};
    \node[circle] at (4, -2.6) {$\dots$};
